Covariate analysis of CMC RNASeq data reprocessed with Star-Feature counts pipeline (ACC and DLPFC with TMM normlaisation and SVA)

### 2016-11-15 code/Rmd/CMC_ACC_And_DLPFC_StarAligned_TMM_SVA.Rmd
Minor bug fix

SURR.VAR = sva::sva(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, MODEL0,
                    block = COVARIATES$Individual_ID, 
                    n.sv = NUM.SV, B = 30)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])

>>>>

SURR.VAR = sva::sva(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, MODEL0,
                    n.sv = NUM.SV, B = 30)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])
